Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-08 report/report.tex
Split up methodology chapter

This section will dive into the state-of-the-art use of city reconstruction methods within the research field of urban design.
This chapter will present the motivations for the digitization of urban planning, as well as the most common programs and tools in this area, which are after all not very commonly used in the practise of urban design due to the failure in being able to reflect the unique workspace of urban designers.
The final section will present a brief history of the field of OpenStreetMap data qualification, and present the research papers whose methods are at the foundation of this project.

@@

\chapter{Methodology and evaluation}

This chapter will present the evaluation metrics that this project served to obtain, and how they relate to the eventual collision analysis.
For the geodata precision study specifically, it will examine how geodata is qualifyied in general, by examining van Oorts quality criteria, and how these will be used in this project.
See section 4 for a detailed technical implementation overview that presents how the relevant metrics were obtained during the statistics collection process.
For the resulting metrics that were obtained, see section 5.

@@

\section{Quality criteria}

@@

@@

Section 4.1 will present the data collection process for the geodata precision study. It will present how to qualify dataset completeness and building correspondence (how many of the buildings in one dataset that can be found in the other) by collecting the cumulative building areas and looking at what buildings have overlapping areas between the two datasets.
The definitions and algorithms neccessary for calculating posiitonal accuracy and a measure for shape accuracy will also be presented.
Section 4.2 will present at the data collection process for the collision study. It will present how standard road withs were obtained, as well as the algorithm for detemining feature collision that was used.
Section 4.3 will discuss briefly the data sources used in this project, why they were chosen and specific issues with the data collection process.

@@

% TODO: Move some of the text from method and evaluation to background
% TODO: Read over the sample report to see what they have in the background section
% TODO: Move the rest of the "method and evaluation" text  into the implementation and evaluations section, perhaps creating a new subsection in the implementation section called "Method"

>>>>

This chapter will dive into the state-of-the-art use of city reconstruction methods within the research field of urban design.
This chapter will present the motivations for the digitization of urban planning, as well as a brief history of the field of OpenStreetMap data qualification, and present the research papers whose methods are at the foundation of this project.
Furthermore, it will present the evaluation metrics that this project served to obtain, and how they relate to the eventual collision analysis.
For the geodata precision study specifically, it will examine how geodata is qualifyied in general, by examining van Oorts quality criteria, and how these will be used in this project.

@@

@@

\subsection{Quality criteria}

@@

This chapter will provide a technical overview of the data collection process and the algorithms used for the purpose of this study, starting with a brief overview in section 4.1.
Section 4.2 will present the data collection process for the geodata precision study. It will present how to qualify dataset completeness and building correspondence (how many of the buildings in one dataset that can be found in the other) by collecting the cumulative building areas and looking at what buildings have overlapping areas between the two datasets.
The definitions and algorithms neccessary for calculating posiitonal accuracy and a measure for shape accuracy will also be presented.
Section 4.3 will present at the data collection process for the collision study. It will present how standard road withs were obtained, as well as the algorithm for detemining feature collision that was used.
Section 4.4 will discuss briefly the data sources used in this project, why they were chosen and specific issues with the data collection process.

@@

@@

% TODO: Read over the sample report to see what they have in the background section
